Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2019-01-29 draft.tex
Phrasing

 \item $j \in A^-$: If we know that agent $j$ prefers $x$ to $y$ then the adversary will place as few alternatives as possible between $x$ and $y$.
 We define $U$ as the set of alternatives that are incomparable with $x$ and $y$ according to $\ppref_i$. Since weights are assumed to be convex, the adversary will place all alternatives in $U$ as better than $x$.
\end{itemize}
In summary, some best completion $\pref$ satisfies two properties: (1) for all $c \pinc x$, $c \pref x$; and (2) for all $c \pinc y$, if not $c \pref x \pref y$ then $y \pref c$. These two properties are intuitively understandable by observing that maximizing the PMR requires placing $x$ as low as possible (hence the first property) and $y$ as high as possible (hence the second property, with the exception that sometimes it is not possible to satisfy both desires and noting that the first desire is more important by convexity of the weights). A proof that this reasoning is correct is in \cref{sec:prfCompl}.

>>>>

 \item $j \in A^-$: If we know that agent $j$ prefers $x$ to $y$ then the adversary will place as few alternatives as possible between $x$ and $y$.
 We define $U$ as the set of alternatives that are incomparable with $x$ and $y$ according to $\ppref_i$. Since weights are assumed to be convex, the adversary will place all alternatives in $U$ as better than $x$.
\end{itemize}
In summary, some best completion $\pref$ satisfies two properties: (1) for all $c \pinc x$, $c \pref x$; and (2) for all $c \pinc y$, if not $c \pref x \pref y$ then $y \pref c$. These two properties are intuitively understandable by observing that maximizing the PMR requires placing $x$ as low as possible, hence the first property; and $y$ as high as possible, hence the second property, with the exception that sometimes it is not possible to satisfy both desires and noting that the first desire is more important by convexity of the weights. A proof that this reasoning is correct is in \cref{sec:prfCompl}.
